Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis

### 2015-09-15 paper/main.tex
Thomas changes in second to last paragraph.

\documentclass[smallextended]{svjour3}
\input{TexOpts.tex}
\begin{document}
\title{Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis}
\author{Edward A. Roualdes \and Simon J. Bonner \and Thomas D. Whitney \and James D. Harwood}
\institute{E.A. Roualdes \and S. J. Bonner
        \at Department of Statistics, University of Kentucky, Rm.~311 Multidisciplinary Science Building, 725 Rose Street, Lexington, KY 40536-0082, \\\email{edward.roualdes@uky.edu} \and
        T.D. Whitney 
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA \emph{Present address: Warnell School of Forestry and Natural Resources, University of Georgia, Athens, GA 30602, USA}
        \and
        J.D. Harwood
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA
}

@@

Beyond the statistical assumptions, sampling issues should be given careful attention.  In collecting prey of interest, we rely on human-made traps.  Human-made traps are liable to collect prey at rates unequal to that of the predator of interest.  Confounded with researchers' abilities to make sufficiently efficient traps are a host of environmental variables.  Researchers should give consideration to these potentialities and attempt to determine to what degree their traps' efficiency is effected.  Mathematically, these issues will directly effect the parameter $c_{st} = \lambda_{st}/\gamma_{st}$.  When human-made traps are relatively more efficient at catching prey than are the predators, $c_{st}$ will be relatively smaller.  Conversely, when the traps are relatively less efficient, $c_{st}$ will be relatively larger.  Unfortunately, these concerns are difficult to control, statistically, practically, or otherwise, and are to some degree unavoidable.

@@

\nocite{Wickham:2011a,Wickham:2011,Bischl:2014,Roualdes:2014}

\bibliographystyle{spbasic}
\bibliography{refs}
\end{document}

>>>>

\documentclass[smallextended]{svjour3}
\input{TexOpts.tex}
\begin{document}
\title{Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis}
\author{Edward A. Roualdes \and Simon J. Bonner \and Thomas D. Whitney \and James D. Harwood}
\institute{E. A. Roualdes \and S. J. Bonner
        \at Department of Statistics, University of Kentucky, Rm.~311 Multidisciplinary Science Building, 725 Rose Street, Lexington, KY 40536-0082, \\\email{edward.roualdes@uky.edu} \and
        T.D. Whitney 
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA \emph{Present address: Warnell School of Forestry and Natural Resources, University of Georgia, Athens, GA 30602, USA}
        \and
        J.D. Harwood
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA
}

@@

Beyond the statistical assumptions, sampling of prey availability should be given careful attention.  To survey prey of interest, we relied on pitfall trapping, which is a reasonable method to quantify potential prey encounters of sit-and-pursue predators, such as wolf spiders \citep{Uetz:1999}.  In general, however, human-made traps are liable to collect prey at rates unequal to that of the predator of interest.  Confounded with researchers' abilities to make sufficiently efficient traps are a host of environmental variables.  Researchers should consider these potential sampling issues and attempt to determine, a priori, how well their traps will characterize prey availability according to the biology of their focal predator.  Mathematically, these issues will directly affect the parameter $c_{st} = \lambda_{st}/\gamma_{st}$.  When human-made traps are relatively more efficient at catching prey than are the predators, $c_{st}$ will be relatively smaller.  Conversely, when the traps are relatively less efficient, $c_{st}$ will be relatively larger.  Unfortunately, these factors can be difficult to control, statistically, practically, or otherwise, and are to some degree unavoidable.

@@

\nocite{Wickham:2011a,Wickham:2011,Bischl:2014,Roualdes:2014}
\bibliographystyle{spbasic}
\bibliography{refs}
\end{document}
